Lineage Analysis of CRISPR and shRNA Screens

### 2018-08-30 lineages_18Q3.Rmd

Load libraries.
```{r}
library(NMF)
library(ggpubr)
library(rowr)
library(data.table)
library(CePa)
library(plyr)
library(tidyverse)
library(magrittr)
library(matrixStats)
library(parallel)
library(kableExtra)
library(gridExtra)
library(broom)
library(glmnet)
library(devtools)
library(reshape2)
library(caret)
library(bsselectR)
library(ComplexHeatmap)
library(circlize)
```

@@

  # Copy number
  lo_cn <- range(gene$Copy_Number[!is.na(gene$Copy_Number)])[1]
  hi_cn <- range(gene$Copy_Number[!is.na(gene$Copy_Number)])[2]
  mid_cn <- (hi_cn - lo_cn) / 2
  plot_cn <- ggplot(data = gene, aes(x = Copy_Number, y = Score, color = Mutation_Status)) +
    geom_point(size = 0.5, alpha = 0.5) +
    geom_smooth(method = "lm", size = 0.5) +
    geom_hline(yintercept = 0, linetype = 2, lwd = 0.3) +
    scale_color_manual(values = crispr_color) +
    stat_cor(method = "pearson", show.legend = FALSE, label.x = c((lo_cn + mid_cn) / 2, (hi_cn - mid_cn) / 2 + mid_cn), label.y = max(gene$Score)) +
    theme(legend.position = "none") +
    labs(y = "CERES Score", color = "Mutation Status",
         x = paste0(g, " Copy number"), title = "Copy Number",
         subtitle = "r: Pearson correlation coeffcient")

@@

@@

###  Metadata exploration

@@

# Convert log2 ratios (log2(CN/2)) to CN
# cn[2:ncol(cn)] <- lapply(cn[2:ncol(cn)], function(x) 2 * (2 ^ x))

@@

@@

@@

```{r}
crispr_data <- readRDS("./../crispr_lineages_giant_files/crispr_data_18Q3.rds")
crispr_ccl <- data.frame("Broad_ID" = crispr_data$Broad_ID)
write.table(crispr_data[, c("Hugo_Symbol", "Broad_ID", "Score", "Primary.Disease", "primary_tissue", "Mutation_Status")], file = "~/Desktop/crispr_data_select.tsv", quote = FALSE, sep = "\t")
```

@@

# Mutation exploration

@@

@@

```{r fig.height=6, fig.width=12}
ggplot(data = maf_annot, aes(x = primary_tissue, y = n)) +
  geom_jitter(alpha = 0.6, size = 0.7, position = position_jitter(w = 0.15)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

@@

knitr::kable(filter(crispr_signif, p < 0.1)[, c(1, 5, 6, 7, 8, 10)], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines, p < 0.1 (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```

@@

knitr::kable(filter(crispr_signif_lineage, p < 0.1)[, c(1, 2, 5, 6, 7, 8, 10)], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines by Lineage, p < 0.1 (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```

@@

```{r, eval=TRUE}
crispr_signif_tissue <- compare_means(Score ~ Mutation_Status, group.by = c("Hugo_Symbol", "primary_tissue"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_tissue <- adj_signif(crispr_signif_tissue)
# crispr_signif_tissue <- mutate(crispr_signif_tissue, primary_tissue = reorder(primary_tissue, p.adj, mean))
crispr_signif_tissue <- crispr_signif_tissue[order(crispr_signif_tissue$p),]
saveRDS(crispr_signif_tissue, "./data_munging/rds/crispr_signif_tissue.rds")
```

@@

knitr::kable(filter(crispr_signif_tissue, p < 0.1)[, c("Hugo_Symbol", "primary_tissue", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines by Primary Tissue, p < 0.1 (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```

@@

knitr::kable(filter(shrna_signif, p < 0.1)[, c(1, 5, 6, 7, 8, 10)], caption = "shRNA Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines, p < 0.1  (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```

@@

```{r}
mean(chm_cn_cgc[!is.na(chm_cn_cgc)])
```

@@

chm_plot_cgc <- Heatmap(chm_scores_cgc, name = "CERES Score",
        bottom_annotation = HeatmapAnnotation(df = chm_annot),
        bottom_annotation_height = unit(5, "in"),
        row_title = "Genes", column_title = "Cancer Cell Lines",
        col = colorRamp2(c(min(chm_scores_cgc), 0, max(chm_scores_cgc)), c("purple4", "white", "seagreen4")),
        na_col = "black",
        row_title_gp = gpar(fontsize = 60, fontface = "bold"),
        row_names_gp = gpar(fontsize = 10),
        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
        column_names_gp = gpar(fontsize = 8),
        row_dend_reorder = TRUE,
        column_dend_reorder = TRUE,
        clustering_distance_rows = "euclidean",
        clustering_distance_columns = "euclidean",
        clustering_method_rows = "complete",
        clustering_method_columns = "complete",
        column_dend_height = unit(4, "in"),
        row_dend_width = unit(4, "in"),
        width = 3)

@@

pdf("./plots_18Q3/crispr_heatmap_euclidean_all_cgc.pdf", width = 100, height = 100, paper = "special")
draw(chm_all_plot_cgc, heatmap_legend_side = "right", annotation_legend_side = "right")
seekViewport("annotation_Cell_Line_SSMD")
grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Cas9_Activity")
grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Culture_Type")
grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Tissue")
grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Disease")
grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Gender")
grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Source")
grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
dev.off()
```

@@

>>>>

Load libraries.
```{r}
library(NMF)
library(ggpubr)
library(ggsignif)
library(rowr)
library(data.table)
library(CePa)
library(plyr)
library(tidyverse)
library(magrittr)
library(matrixStats)
library(parallel)
library(kableExtra)
library(gridExtra)
library(broom)
library(glmnet)
library(devtools)
library(reshape2)
library(caret)
library(bsselectR)
library(ComplexHeatmap)
library(circlize)
```

@@

  # Copy number
  lo_cn <- range(gene$Copy_Number[!is.na(gene$Copy_Number)])[1]
  hi_cn <- range(gene$Copy_Number[!is.na(gene$Copy_Number)])[2]
  mid_cn <- (hi_cn - lo_cn) / 2
  plot_cn <- ggplot(data = gene, aes(x = Copy_Number, y = Score, color = Mutation_Status)) +
    geom_point(size = 0.5, alpha = 0.5) +
    geom_smooth(method = "lm", size = 0.5) +
    geom_hline(yintercept = 0, linetype = 2, lwd = 0.3) +
    scale_color_manual(values = crispr_color) +
    stat_cor(method = "pearson", show.legend = FALSE, label.x = c((lo_cn + mid_cn) / 2, (hi_cn - mid_cn) / 2 + mid_cn), label.y = max(gene$Score)) +
    theme(legend.position = "none") +
    labs(y = "CERES Score", color = "Mutation Status",
         x = paste0(g, " Theoretical Copy number"), title = "Copy Number",
         subtitle = "r: Pearson correlation coeffcient")

@@

### Make tissue plot

```{r}
makeCRISPRtissueplot <- function(g) {
  sig <- filter(crispr_signif_tissue, Hugo_Symbol == g)
  if(nrow(sig) == 0) {
    return(NULL)
  }
  else {
    gene <- filter(crispr_data, Hugo_Symbol == g)
    gene <- merge(gene, sig, by = c("Hugo_Symbol", "primary_tissue"))
    gene <- mutate(gene, primary_tissue = reorder(primary_tissue, p, mean))
    crispr_color <- as.character(gene$Color)
    names(crispr_color) <- gene$Mutation_Status
    score_range <- abs(range(gene$Score)[2] - range(gene$Score)[1])
    round_accuracy <- ifelse(score_range <= 2, 0.25,
                             ifelse(score_range <= 3, 0.5, 1.0))

    plot <- ggplot(data = gene, aes(x = primary_tissue, y = Score)) +
      geom_point(alpha = 0.5, mapping = aes(color = Mutation_Status)) +
      scale_color_manual(values = crispr_color) +
      coord_cartesian(y = c(min(gene$Score), round_any(x = max(gene$Score), accuracy = round_accuracy, f = ceiling))) +
      geom_signif(data = gene, mapping = aes(xmin = primary_tissue, xmax = primary_tissue, annotations = paste(p.short, "\n", p.adj.short), y_position = max(gene$Score)), manual = TRUE, tip_length   = 0, size = 0, textsize = 3) +
      theme(legend.position = "top", axis.text.x = element_text(angle = 70, hjust = 1, size = 10)) +
      labs(y = "CERES Score",
           x = "Primary Tissue",
           color = "Mutation Status",
           title = paste0(g, ": CERES score by cell line primary tissue"),
           subtitle = "Primary tissues sorted by increasing p-value; labels indicate unadjusted p-value / BH-corrected p-value.")
    return(plot)
  }
}
```

@@

@@

# Convert log2 ratios (log2(CN/2)) to CN
cn[2:ncol(cn)] <- lapply(cn[2:ncol(cn)], function(x) 2 * (2 ^ x))

@@

## CRISPR dependency probabilities

```{r}
dep <- read.delim("./data_munging/gene_dependency_18Q3.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
# Remove Entrez gene IDs from colnames
colnames(dep) <- gsub(" .*", "", colnames(dep))
```

@@

# Melt dependency probabilities dataset for merging
dep_melt <- melt(dep, id.vars = "Broad_ID", measure.vars = colnames(dep)[2:ncol(dep)], variable.name = "Hugo_Symbol", value.name = "Dep_Prob")

# Merge dependency probabilities
crispr_melt <- merge(crispr_melt, dep_melt, by = c("Broad_ID", "Hugo_Symbol"), all.x = TRUE)

@@

```{r}
crispr_data <- readRDS("./../crispr_lineages_giant_files/crispr_data_18Q3.rds")
crispr_ccl <- data.frame("Broad_ID" = crispr_data$Broad_ID)
# write.table(crispr_data[, c("Hugo_Symbol", "Broad_ID", "Score", "Primary.Disease", "primary_tissue", "Mutation_Status")], file = "~/Desktop/crispr_data_select.tsv", quote = FALSE, sep = "\t")
```

@@

# Exploration

@@

##  Metadata

## Mutations

@@

```{r fig.height=3, fig.width=6}
ggplot(data = maf_annot, aes(x = primary_tissue, y = n)) +
  geom_jitter(alpha = 0.6, size = 0.7, position = position_jitter(w = 0.15)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Distribution of mutations across cell lines and primary tissues", subtitle = "Each data point represents a single cell line.", x = "Primary Tissue", y = "Number of Mutations")
```

## Dependency probabilities

```{r fig.height=3, fig.width=6}
ggplot(data = crispr_data, aes(x = Dep_Prob)) +
  geom_histogram(breaks = seq(0, 1, by = 0.05), fill = "darkslategray3", color = "black", alpha = 0.7) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
  scale_y_continuous(breaks = seq(0, 5500000, by = 500000), labels = formatC(seq(0, 5500000, by = 500000), format = "d")) +
  stat_bin(breaks = seq(0, 1, by = 0.05), geom = "text", colour = "black", size = 3.5, aes(label = ..count..), vjust = -1) +
  labs(title = "Distribution of all dependency probabilities", x = "Probability of Real Dependency", y = "Frequency")
```

```{r}
dep95 <- filter(crispr_data, Dep_Prob >= 0.95)
```

```{r fig.height=6, fig.width=8}
ggplot(data = dep95, aes(x = Dep_Prob)) +
  geom_histogram(mapping = aes(fill = primary_tissue), breaks = seq(0.95, 1, by = 0.005), color = "black", alpha = 0.7) +
  scale_y_continuous(breaks = seq(0, 60000, by = 10000), labels = formatC(seq(0, 60000, by = 10000), format = "d")) +
  theme(legend.position = "bottom") +
  guides(fill = guide_legend(nrow = 3, byrow = FALSE)) +
  stat_bin(breaks = seq(0.95, 1, by = 0.005), geom = "text", color = "black", size = 3.5, aes(label = ..count..), vjust = -1) +
  labs(title = "Distribution of all dependency probabilities > 0.95", x = "Probability of Real Dependency", y = "Frequency", fill = "Primary Tissue")
```

@@

knitr::kable(filter(crispr_signif, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines, p < 0.1 (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```

@@

knitr::kable(filter(crispr_signif_lineage, p < 0.05)[, c("Hugo_Symbol", "lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines by Lineage, p < 0.1 (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```

@@

```{r, eval=FALSE}
crispr_signif_tissue <- compare_means(Score ~ Mutation_Status, group.by = c("Hugo_Symbol", "primary_tissue"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_tissue <- adj_signif(crispr_signif_tissue)
# crispr_signif_tissue <- mutate(crispr_signif_tissue, primary_tissue = reorder(primary_tissue, p.adj, mean))
crispr_signif_tissue <- crispr_signif_tissue[order(crispr_signif_tissue$p),]
saveRDS(crispr_signif_tissue, "./data_munging/rds/crispr_signif_tissue.rds")
```

@@

knitr::kable(filter(crispr_signif_tissue, p < 0.05)[, c("Hugo_Symbol", "primary_tissue", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines by Primary Tissue, p < 0.1 (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```

@@

knitr::kable(filter(shrna_signif, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "shRNA Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines, p < 0.1  (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```

@@

```{r}
colnames(chm_annot)
```

@@

chm_annot_list <- HeatmapAnnotation(df = chm_annot,annotation_legend_param = list(Primary_Disease = list(nrow = 6, title = "Primary Disease", title_position = "topleft"), Primary_Tissue = list(nrow = 6, title = "Primary_Tissue", title_position = "topleft"), Culture_Type = list(nrow = 6, title = "Culture Type", title_position = "topleft"), Source = list(nrow = 6, title = "Source", title_position = "topleft")))

chm_plot_cgc <- Heatmap(chm_scores_cgc, name = "CERES Score",
        bottom_annotation = chm_annot_list,
        bottom_annotation_height = unit(5, "in"),
        row_title = "Genes", column_title = "Cancer Cell Lines",
        col = colorRamp2(c(min(chm_scores_cgc), 0, max(chm_scores_cgc)), c("purple4", "white", "seagreen4")),
        na_col = "black",
        row_title_gp = gpar(fontsize = 60, fontface = "bold"),
        row_names_gp = gpar(fontsize = 10),
        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
        column_names_gp = gpar(fontsize = 8),
        row_dend_reorder = TRUE,
        column_dend_reorder = TRUE,
        clustering_distance_rows = "euclidean",
        clustering_distance_columns = "euclidean",
        clustering_method_rows = "complete",
        clustering_method_columns = "complete",
        column_dend_height = unit(4, "in"),
        row_dend_width = unit(4, "in"),
        width = 3)

@@

pdf("./plots_18Q3/crispr_heatmap_euclidean_all_cgc.pdf", width = 100, height = 100, paper = "special")
draw(chm_all_plot_cgc, heatmap_legend_side = "bottom", annotation_legend_side = "bottom")
seekViewport("annotation_Cell_Line_SSMD")
grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Cas9_Activity")
grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Culture_Type")
grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Tissue")
grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Disease")
grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Gender")
grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Source")
grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
dev.off()
```

@@

## Sorted tissue plots

```{r fig.height=12, fig.width=12, include=FALSE}
makeCRISPRtissueplot("KRAS")
```

Plot code:
```{r, eval=FALSE}
crispr_data_cgc <- filter(crispr_data, Hugo_Symbol %in% cgc$Hugo_Symbol)
crispr_all_genes <- unique(crispr_data_cgc$Hugo_Symbol)
crispr_all_lins <- lapply(crispr_all_genes, makeCRISPRtissueplot)
crispr_all_lins_paths <- paste0(crispr_all_genes, "_crispr_tissue.png")
pwalk(list(crispr_all_lins_paths, crispr_all_lins), ggsave, path = "./plots_18Q3/crispr_tissue_plots_cgc", dpi = 300, width = 12, height = 12, units = "in")
```

Data management:
```{r}
crispr_all_bygene <- paste0(list.files("./plots_18Q3/crispr_tissue_plots_cgc", full.names = TRUE))
names(crispr_all_bygene) <- str_replace_all(crispr_all_bygene, c("_crispr_tissue.png" = "", "./plots_18Q3/crispr_tissue_plots_cgc/" = ""))
crispr_bygene_order <- c(intersect(crispr_signif$Hugo_Symbol, names(crispr_all_bygene)), setdiff(names(crispr_all_bygene), crispr_signif$Hugo_Symbol))
crispr_all_bygene <- crispr_all_bygene[match(crispr_bygene_order, names(crispr_all_bygene))]
bsselect(crispr_all_bygene, type = "img", selected = "KRAS", live_search = TRUE, show_tick = TRUE, height = 300, frame_height = 275)
```
